Deployable Probabilistic Programming

### 2019-04-15 paper/paper.tex
in progress

\title{Server-Side Probabilistic Programming}
\author{David Tolpin}
\affiliation{
    \institution{PUB+}
    \country{Israel}
}
\email{david.tolpin@gmail.com}

@@

\section{Challenges of Server-Side Probabilistic Programming}

@@

\section{Guidelines to Implementation of a Probabilistic Programming Facility}

@@

In line with the guidelines, we have implemented a probabilistic
programming facility for the Go programming language,
Infergo. %(\url{http://infergo.ml/}).
We have chosen Go because Go is a small but expressive
programming language with efficient implementation, which has
recently become quite popular for computation-intensive
server-side programming.  the time of writing, the
implementation is still at an early stage.  This facility
ialready used in production environment for inference of
mission-critical algorithm parameters.

@@

@@

>>>>

\title{Deployable Probabilistic Programming}
\author{David Tolpin}
\affiliation{
    \institution{PUB+}
    \country{Israel}
}
\email{david.tolpin@gmail.com}

@@

\section{Challenges}

@@

\section{Guidelines}

@@

In line with the guidelines, we have implemented a probabilistic
programming facility for the Go programming language, Infergo.
%(\url{http://infergo.ml/}). 
We have chosen Go because Go is a
small but expressive programming language with efficient
implementation, which has recently become quite popular for
computation-intensive server-side programming. Infergo is
used in production environment for inference of mission-critical
algorithm parameters.

@@

\subsubsection{Optimization}

\subsubsection{Full Posterior}

@@

The author owes a debt of gratitude to Frank Wood who introduced
the author to probabilistic programming and inspired to
pursue probabilistic programming paradigms and applications. The
author also would like to thank Jan-Willem van de Meent, with
whom the author had fruitful discussions of motives, ideas, and
implementation choices behind Infergo, and whose thoughts and
recommendations significantly influenced Infergo design.
Finally, the author thanks PUB+, the company the author works
for, for supporting development of Infergo and letting the
author experiment with applying probabilistic programming to
critical decision-making in production environment.
